Reading Notes

### 2020-07-17 reading-notes.tex
reading Moore and writing about CG potential dev

>>>>

\cite{Moore2014}
IBI that includes data from multiple targets to yield a less state dependent potential.
i feel pretty confident in my understanding of ibi after making my own MWE
how are the state points combined?
separate potentials are required to capture solid and fluid structures of a pure simple lipid ref 46
IBI potentials are sometimes transferrable and it is not clear why sometimes they are and sometimes they aren't.
the potentials are an average, basically of the potentials at the different states with a weighting function to put emphasis on the desired state
Don't pick states that are too similar because then the overlap region is too large and there are too many possible solutions. for some systems there may not be a potential that represents all states-- this is not unique to coarse potentials, atomistic potentials also have this limitation.
